---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

# zhbs_dms

<!-- badges: start -->
<!-- badges: end -->

## Objectives 🎯

The data management system aims to automate several otherwise manual data operations:

1. Acquisition
1. Reporting
1. Processing

For data acquisition, the system:

- **Downloads.** For target questionnaire(s), obtains data for every version (e.g., v1, v2, ..., vN) 
- **Combines.** For each questionnaire, combines data from multiple versions into a single set of data files containing all observations.
- **Constructs.** For certain questionnaires, creates data files in more convenient form than exported (e.g., a single file for food consumption rather than one for each food group).

For data reporting, the system:

- **Inventories** the data received by primary sampling unit, flagging cases with data shortfalls
- **Monitors** trends in survey microdata that could undercut key survey indicators
- **Analyses** trends in survey paradata that could indicate problems (e.g., short interviews, answer changes, etc.)

For data processing, the system:

- **Checks** for issues in incoming interview data.
- **Recommends** what to do with each interview: approve, review, reject, discuss with field staff due to persisent problems.
- **Executes** the process for rejection, if desired. This entails 
- **Reports** on identified issues in two ways. First, by creating files the flagged issues. Second, by generating a report of the top issues, the top reasons for rejection, and the number of rejections.

**NOTE:** as of `r Sys.Date()`, only the data acquition and data processing functions have been implemented

## Installation 💻🔌 

- [Install dependencies](#install-dependencies)
- [Clone repository](#clone-repository)
- [Provide parameters](#provide-parameters)

<details>
<summary>See detailed installation instructions 👁📑</summary>

### Install dependencies

Before running this program for the first time, (re)install the
following software:

- [R](#r)
- [RTools](#rtools)
- [RStudio](#rstudio)

Even if these software packages are already installed, it is necessary
to reinstall them in order to have the latest version of these tools for
this program to work successfully.

Please read below about how to install these programs.

#### R

- Follow this [link](https://cran.r-project.org/)
- Click on the appropriate link for your operating system
- Click on `base`
- Download and install (e.g., [this](https://cran.r-project.org/bin/windows/base/R-4.3.2-win.exe) for Windows)

#### RTools

Required for the Windows operating system.

- Follow this [link](https://cran.r-project.org/)
- Click on `Windows`
- Click on `RTools`
- Download (e.g.,[this](https://cran.r-project.org/bin/windows/Rtools/rtools43/files/rtools43-5863-5818.exe)for a 64bit system)
- Install in the default installation location (e.g., `C:\rtools43` on Windows)

This program allows R to compile C++ scripts used by certain packages
(e.g., `{dplyr}`).

#### RStudio

- Follow this [link](https://posit.co/products/open-source/rstudio/)
- Click on the `DOWNLOAD RSTUDIO` button in the upper right-hand corner of the page's navbar
- Click on the appropriate link for your operating system
- Download and install (e.g., [this](https://download1.rstudio.org/electron/windows/RStudio-2023.09.1-494.exe) for Windows)

### Clone repository

- Click on the `<> Code` button
- Select the best method for copying the project from GitHub to your device. For most, this will be the clicking on `Download ZIP`, downloading, and unzipping.

### Provide parameters

#### Provide Survey Solutions connection details

```{r}
#| label: server connection details
server      <- "" # provide the complete URL of the server
workspace   <- "" # use the name that is an ID rather than the display name
user        <- "" # note: user must be either admin or API user
password    <- "" # password of the user indicated above

```

#### Identify questionnaires whose data to fetch

```{r}
#| label: identify questionnaires
# provide a string that uniquely identifies the questionnaire. this can be:
# - full name
# - sub-string
# - regular expression

# recall data
qnr_expr_hbs <- ""

# diary record book data
qnr_expr_drb <- ""
```

#### Describe how check issues program should behave

The program allows users to specify three types of behavior

1. Which interview statuses to consider
1. Which issues trigger rejection
1. Whether to reject interviews automatically

##### Which interview statuses to consider

```{r}
#| label: which statuses
# Provide a comma-separated list of interview statuses to review.
# See status values here: 
# https://docs.mysurvey.solutions/headquarters/export/system-generated-export-file-anatomy/#coding_status
#
# Statuses supported by this script include: 
# - Completed: 100
# - ApprovedBySupervisor: 120
# - ApprovedByHeadquarters: 130
statuses_to_reject <- c(100, 120)
```

Here is what each interview status means in the the concrete survey workflow:

| Status                  | Meaning |
|-------------------------|---------|
| Completed               | Marked as complete by an interviewer, but not yet processed by their supervisor |
| ApprovedBySupervisor    | Approved by a supervisor, but not yet processed by headquarters |
| ApprovedByHeadquarters  | Approved by a headquarters |

To have the check issues program act only as headquarters, set `statuses_to_reject <- c(120)`. This will instruct the program to review only those interviews that have been approved by a supervisor and, as such, are ready for headquarters review.

To have the program act simultaneously as both supervisor and headquarters, set `statuses_to_reject <- c(100, 120)`. This default value enables the program to provide feedback on all completed interviews.

##### Which issues trigger rejection

```{r}
#| label: which issue types
# Provide a comma-separated list of issue types to reject
# {susoreview} uses the following codes:
# - 1 = Reject
# - 2 = Comment to post
# - 3 = Survey Solutions validation error
# - 4 = Review
issues_to_reject <- c(1)
```

In the check issues program, issues may have different types. This parameter instructs the program which issues should give rise to rejection. Note that Survey Solutions validation errors are those errors flagged by Survey Solutions and that persist in the data. These latter issues could be minor or major.

##### Whether to reject interviews automatically

```{r}
#| label: whether to reject
# Whether to reject interviews recommended for rejection
# - If TRUE, the program will instruct the server to reject these interviews.
# - If FALSE, the program will not.
# - In either case, the interviews recommended for rejection, 
# and the reasons why, are saved in `/output/`
should_reject <- FALSE
```

The check issues program recommends an action for each interview. For interviews recommended for rejection, the user can specify whether the program should automate the rejection of such interviews--that is, posting comments to those interviews and rejecting them back to the field for explanation and/or remediation.

If the user selects `FALSE`, the program produces the necessary outputs to automate rejection later--potentially of the recommended interviews with additional, human-provided comments.

</details>

## Usage 👩‍💻

- [Open the project](#open-the-project)
- [Check for issues in the HBS recall data](#check-for-issues-in-the-hbs-recall-data)
- [Download the diary record book data](#download-the-diary-record-book-data)

<details>
<summary>See detailed usage instructions 👓👩‍💻</summary>

### Open the project

Before taking any action, open the `zhbs_dms` project as a project. To do so, either open the project in RStudio or double-click on the `zhbs_dms.Rproj` file.

Here, in more detail, is how to do each.

To open the project from within RStudio:

1. Open RStudio
1. Click on `Project: (None)` in the upper right-hand corner
1. Select the project, by either
  - a. Opening the project file
    - Click on `Open Project...`
    - Navigate to `zhbs_dms.Rproj` in the file picker
    - Select `zhbs_dms.Rproj`
    - Click on `Open`
  - b. Selecting the project from the drop-down menu (if previously opened)
1. Wait for RStudio to open the project

To open the project from the `zhbs_dms.Rproj` file:

1. Open your file explorer
1. Navigate to the folder containing `zhbs_dms.Rproj`
1. Double-click on the file
1. Wait for RStudio to open the project

### Check for issues in the HBS recall data

After [opening the project](#open-the-project):

- Open the `run_check_issues.R` file
  - Move to the `Files` tab in RStudio
  - Click on `run_check_issues.R`
- Source the `run_check_issues.R` file
  - Move to the script editor pane where `run_check_issues.R` is open
  - Click on the `Source` button in the upper righthand corner

Once execution has completed:

- Data can be found in `01_get_data/data/hbs/02_combined/`
- Output can be found in `03_check_issues/output/`

### Download the diary record book data

After [opening the project](#open-the-project):

- Open the `get_diary_data.R` file
  - Move to the `Files` tab in RStudio
  - Click on `get_diary_data.R`
- Source the `get_diary_data.R` file
  - Move to the script editor pane where `get_diary_data.R` is open
  - Click on the `Source` button in the upper righthand corner
- Wait for execution to complete

Once execution has completed, the diary data can be found in `01_get_data/data/drb/02_combined/`

</details>
